\documentclass[11pt, notitlepage]{article}
\makeatletter\@addtoreset{section}{part}\makeatother%
\usepackage{amssymb}
\usepackage[margin=1.5cm]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{graphicx} %for graphics
\usepackage{subcaption} %for subfigures
\usepackage{relsize}
\usepackage{xcolor}
\newcommand\myworries[1]{\textcolor{red}{#1}}
\usepackage{titling}
\usepackage[]{algorithm2e}
\usepackage{enumitem}
\usepackage{hyperref}
\newtheorem{example}{Example}[section]
\usepackage{framed}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

\newcommand{\EE}{\ensuremath{\mathbb{E}}}
\newcommand{\NN}{\ensuremath{\mathbb{N}}}
\newcommand{\PP}{\ensuremath{\mathbb{P}}}
\newcommand{\RR}{\ensuremath{\mathbb{R}}}
\newcommand{\dd}{\ensuremath{\mathrm{d}}}
\newcommand{\XX}{\ensuremath{\mathbb{X}}\xspace}
\newcommand{\sX}{\ensuremath{\mathcal{X}}\xspace}
\newcommand{\abs}[1]{\left\lvert{#1}\right\rvert}
\newcommand{\norm}[1]{\left\lVert{#1}\right\rVert}
\newcommand{\var}[1]{\mathrm{var}\left({#1}\right)}
\newcommand{\epvar}[1]{\mathrm{epvar}{\left({#1}\right)}}
\newcommand{\lip}[1]{\ensuremath{\mathrm{Lip}\left({#1}\right)}\xspace}
\newcommand{\rca}[1]{\mathrm{rca}{\left({#1}\right)}}
\newcommand{\tmu}{\ensuremath{\widetilde{\mu}}\xspace}
\newcommand{\tl}{\ensuremath{\widetilde{\lambda}}\xspace}

\newcommand\dhcomment[1]{\textcolor{blue}{\textbf{#1!}}}

\newcommand\rpcomment[1]{\textcolor{red}{\textbf{#1!}}}
\title{Gelation Behaviour for Kac interaction clusters}
\author{RP, DH}
\date{\today}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem*{intuition}{Physical Intuition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{formula}{Formula}[section]
\newtheorem{conjecture}{Conjecture}
\newtheorem{observation}[conjecture]{Observation}
%\newtheorem{remark}[theorem]{Remark}


\begin{document}

\maketitle

\input{introduction.tex}
\input{Statements_of_results.tex}
\input{Analysis_of_Smoluchowski_Equation.tex}
\input{Convergence_of_the_Stochastic_Coalescent.tex}
\input{Introduction_to_Random_Graphs.tex}
\input{Coupling_to_random_graphs.tex}
\input{Equality_of_Critical_times.tex}
\input{Finiteness_of_second_moment_after_tgel.tex}
\input{Uniform_Convergence_of_Stochastic_Coagulant.tex}
\input{Size_Biasing_effect.tex}
\input{Convergence_of_Gel.tex}
\input{kinetic.tex}


\begin{thebibliography}{}
\bibitem{D&N} Darling, R.W.R. and Norris, J.R., 2008. Differential equation approximations for Markov chains. Probability surveys, 5, pp.37-79.

\bibitem{HPR16} Heida, M. and Patterson, R.I.A. and Renger, D.R,M., 2016. WIAS Preprint 2353

\bibitem{Meg} Megginson, R.M., An introduction to Banach space theory,

\bibitem{PSW17} Patterson, R.I.A and Simonella, S. and Wagner, W., 2017. A Kinetic Equation for the Distribution of Interaction Clusters in Rarefied Gases, J. Stat. Phys., 

\bibitem{BJR07} Bollob\'as, B., Janson, S. and Riordan, O., 2007. The phase transition in inhomogeneous random graphs. Random Structures \& Algorithms, 31(1), pp.3-122.

\bibitem{N00} Norris, J.R., 2000. Cluster coagulation. Communications in Mathematical Physics, 209(2), pp.407-435.

\bibitem{N99} Norris, J.R., 1999. Smoluchowski's coagulation equation: Uniqueness, nonuniqueness and a hydrodynamic limit for the stochastic coalescent. Annals of Applied Probability, pp.78-109.

\bibitem{K02} Kallenberg, O., 2002. Foundations of modern probability, 2.ed., Springer

\bibitem{L78} Lushnikov, A. A., 1978. Coagulation in finite systems.  Journal of Colloid and Interface Science, pp.276--285.

\bibitem{A99} Aldous, D. J., 1999. Deterministic and stochastic models for coalescence (aggregation and coagulation): a review of the mean-field theory for probabilists. Bernoulli, pp.3--48.  

\bibitem{K56} Kac, M., 1956. Foundations of kinetic theory. In: Third Berkeley Symposium on Mathematical Statistics and Probability Theory, vol. 3, pp. 171--197. University of California Press, Berkeley. 

\bibitem{GKSZ08} Gabrielov, A., Keilis-Borok, V., Sinai, Y., Zaliapin, I., 2008. Statistical properties of the cluster dynamics of the systems of statistical mechanics. In: Boltzmann’s Legacy. ESI Lect. Math. Phys., pp.203--215. Eur.
Math. Soc., Zürich

\bibitem{vS16} von Smoluchowksi, M., 1916. Drei Vorträge über Diffusion, Brownsche Molekularbewegung und Koagulation von Kolloidteilchen. Physikalische Zeitschrift, pp585--599.
\end{thebibliography}


\end{document}
